---
title: "Paul Vernus's CV"
author:
  firstname: Paul
  lastname: Vernus
  address: "12 avenue d'Italie, 63000 Clermont-Ferrand, France"
  position: "Phd candidate in Economics"
  contacts:
    - icon: fa envelope
      text: paul.vernus@ferdi.fr
      url: "mailto:paul.vernus@ferdi.fr"
    # - icon: assets/icon/bi-house-fill.svg
    #   text: website.com
      # url: https://website.com
    # - icon: fa brands orcid
    #   text: 0000-0000-0000-0000
    #   url: https://orcid.org/0000-0000-0000-0000
    - icon: fa brands linkedin
      text: LinkedIn
      url: https://www.linkedin.com/in/paul-vernus-09538214b/
    - icon: fa brands github
      text: GitHub
      url: https://github.com/pvernus      
    # - icon: fa brands x-twitter
    #   text: twitter
    #   url: https://twitter.com/example
format: awesomecv-typst
brand:
  typography: 
    fonts:
      - family: Roboto
        source: google
        weight: [100, 400, 700]
      - family: Source Sans 3
        source: google
        weight: [100, 400, 700]
        style: [normal, italic]
    base: Source Sans 3
  color:
    primary: "#832b6d"
    link: "#5c1e4c"
  defaults:
    awesomecv-typst:
      font-header: Roboto
execute: 
  echo: false
  warning: false
---

```{r setup, include=FALSE}
library(typstcv)
library(tidyverse)
library(lubridate)
```

**Focus**: Political economy • Foreign aid delivery • Geopolitics of climate • Data analysis & causal inference

## Work Experience

```{r}
#| output: asis
read_delim(
  file = "data/work.csv",
  delim = ";",
  locale = locale(encoding = "WINDOWS-1252"),
  escape_double = FALSE, 
  col_types = cols(start = col_date(format = "%d/%m/%Y"), 
                   end = col_date(format = "%d/%m/%Y")), 
  trim_ws = TRUE) |> 
  format_date(end = "end") |>
  resume_entry(title = "employer",
               location = "location",
               description = "position", 
               details = c("detail1", "detail2", "detail3"))
```


## Education

```{r}
#| output: asis
read_delim(
  file = "data/education.csv",
  delim = ";",
  locale = locale(encoding = "WINDOWS-1252"),
  escape_double = FALSE, 
  col_types = cols(start = col_date(format = "%d/%m/%Y"), 
                   end = col_date(format = "%d/%m/%Y")), 
    trim_ws = TRUE) |> 
  format_date(end = "end") |>
  resume_entry(title = "degree", 
               description = "institution", 
               details = c("detail1", "detail2"))

```

## Languages and Certifications

```{r}
#| output: asis
read_delim("data/skill.csv", 
           delim = ";", 
           locale = locale(encoding = "WINDOWS-1252"),
           escape_double = FALSE, 
           trim_ws = TRUE) |> 
  resume_entry(
    title = "skill",
    description = "language",
    details = c("detail1", "detail2", "detail3", "detail4", "detail5", "detail6")
               )
```

## References

- **Vianney Dequiedt**: Professor in economics at CERDI-UCA and Scientific Director at FERDI.
  - *Contact: vianney.dequiedt@uca.fr*
- **Fleur Wouterse**: Deputy Director Office of Emergencies and Resilience, FAO. 
  - *Contact: fleur.wouterse@fao.org*
- **Catherine Simonet**: Lead Adaptation Expert, AFD.
  - *Contact: simonetc@afd.fr*
- **Pascal Furth**: Head of Economic Affairs, French Embassy in Cairo, French Treasury. 
  - *Contact: pascal.furth@dgtresor.gouv.fr*
